Response to the defense feedback

### 2021-06-02 Chapter-6/Chapter-6.tex
Updates from Overleaf

\subsection*{Design Choices} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} times out after several days. The profiling result showed that the tool spent most its time in Z3. Later, we used a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
This paper presents an approach that tries to give a conservative
estimate of the amount of leaked information by address-based
side-channel attacks. These attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although these kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of these vulnerabilities, developers
do not fix them because they think these side-channel vulnerabilities
are not important. To show the importance of these side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of these side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report severe leakage, it does not mean the program has a truly
severe leakage.

>>>>

\subsection*{Design Choices} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} timed out after several days. The profiling result showed that the tool spent most its time in Z3. Later, we used a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

@@

\tool{} reaches full precision if the number of estimated leaked bits
equals to Definition~\ref{chapter4:def}.
\tool{} may lose precision from the
memory model it uses in theory. However, we did not find false positives
caused by the imprecise memory model during our evaluation.
Sampling introduces imprecision but with a probabilistic guarantee.
However, during the evaluation, we find that \tool{} cannot estimate
the amount of leakage for some leakage sites in a reasonable time,
which means the number of $K^o$ is very small. According to Definition~\ref{chapter4:def}, it means the leakage is very severe. 
\section{Precise Analysis on Multiple-trace Attacks}
In this work, we present an approach that tries to give a 
estimation of the amount of leaked information by access-based
side-channel attacks. These attacks exploit the data-flow from secrets
to load address and the data-flow from the data-flow from secrets to
branch conditions to retrieve secrets based on the observation on the
memory accesses. Although these kinds of side-channel leakages have
been discovered for decades, the up-to-date software still has some
side-channel leakages. For some of these vulnerabilities, developers
do not fix them because they think these side-channel vulnerabilities
are not important. To show the importance of these side-channel
leakages, one way is to demonstrate an end-to-end attack based on the
vulnerability. However, demonstrating an end-to-end attack often need
a lot of manual effort and the domain knowledge of the victim program,
which is not often the case in practice. It is good to have a tool
that automatically assesses the severity level of these side-channel
leakages. So it would be better to have a proper metric to quantify
the side-channel leakage. However, we find previous side-channel
quantification tools are developed to ensure the noninterference of
the program. They use the over-approximation heuristics method to
quantify the leakage. For example, CacheAudit estimates that a 128-bit
AES encryption can leak more than 128 bits. As a result, even these
tools report severe leakage, it does not mean the program has a truly
severe leakage.
